Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-04 inc/hardware/magnetic_lenses/maglens.tex
merge remaining comments on mag_lens design. still need to tweak build schematic

For the UEM system at UIC, two of these lenses are employed to manage the divergence created by an RF cavity and focus the pulses to a focal spot. 
These lenses are positioned one before and one after the cavity, forming a lens system of a combined effective focal length.
For the purposes of design, one can make a reasonable approximation that the two lenses together may together provide the total necessary number of amp-turns.
As each lens has 100 turns, a current of only about 2A is needed to drive the two lenses in series.
A picture of this system is shown in \ref{fig:maglens-pic}.
In that picture the two lenses are shown, however a placeholder is shown inserted between them rather than an actual RF cavity.

@@

%TODO need reference for equation and \alpha_{Cu}
Since the lenses have no active cooling system, it was prudent to characterize the thermal response to a moderate current load.
Resistance of metals changes as a function of temperature by $ R = R_0 [ 1 + \alpha ( T - T_0 ) ] $, where $\alpha$ is a material contant; for copper, $\alpha = 3.9 * 10^{-3} \text{K}^{-1}$. 
One can calculate the temperature increase of the system by monitoring the change in resistance.
Maintaining a constant current of 4A through the lens, the voltage drop increased from 1.22V ($R_0 = 0.305\Omega$) to 1.25V ($R=0.3125\Omega$) as the lens warmed.
The resultant temperature increase is only $T - T_0 = 2\text{K}$.
This result is easily confirmed manually; the oxygen-free copper wire coils remain cool to the touch under these operating conditions.

>>>>

For the UEM system at UIC, two of these lenses are employed to manage the divergence created by an RF cavity and the anode aperture, then focus the pulses to a focal spot. 
These lenses are positioned one before and one after the RF cavity, forming a lens system of a combined effective focal length; the two lenses are wound oppositely to counteract beam rotation.
For the purposes of design, one can make a reasonable approximation that the two lenses together provide the total necessary number of amp-turns.
As each lens has 100 turns, a current of only about 2A is needed to drive the two lenses in series to attain a 4in focal length.
A picture of this system is shown in \ref{fig:maglens-pic}.
In that picture the two lenses are shown, however a placeholder is shown inserted between them rather than an actual RF cavity.

@@

%TODO need reference for equation and \alpha_{Cu}
As the lenses have no active cooling system, it was prudent to characterize the thermal response to a moderate current load.
Resistance of metals changes as a function of temperature by $ R = R_0 [ 1 + \alpha ( T - T_0 ) ] $, where $\alpha$ is a material contant; for copper, $\alpha = 3.9 * 10^{-3} \text{K}^{-1}$. 
One can calculate the temperature increase of the system by monitoring the change in resistance.
Maintaining a constant current of 4A through the lens, the voltage drop increased from 1.22V ($R_0 = 0.305\Omega$) to 1.25V ($R=0.3125\Omega$) as the lens warmed.
The resultant temperature increase is only $T - T_0 = 2\text{K}$.
This result is easily confirmed manually; the oxygen-free copper wire coils remain cool to the touch under these operating conditions.
